---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# easymlr

<!-- badges: start -->
[![R-CMD-check](https://github.com/UBC-MDS/easymlr/workflows/R-CMD-check/badge.svg)](https://github.com/UBC-MDS/easymlr/actions)
<!-- badges: end -->

easymlr is an open-source library designed to perform exploratory data analysis, to help with missing data imputation and to give baseline models. Also, it assists in feature selection which is a common problem when undertaking a data science or machine learning analysis. As it's name indicates, this function performs all task from eda to helping in choosing model for machine learning process very easily.

## Installation

Package installation in R:

The development version can be found in [Github](https://github.com/).

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("UBC-MDS/easymlr")
```

## Features

This package introduces a data science enthusiast, with little to no knowledge of machine learning, to the common steps required when undertaking a Supervised learning analysis. The package contains four functions that taken in data and perform a task. All functions can be used on a dataset with numerical features. Each function has their own required arguements and optional arguments, with some default parameters.

- **eda_analysis**: The `eda_analysis` function will split the original data into train and test dataset and will generate a statistical report such as correlation between the variables, number of missing data, class imbalance and type of data present in the dataset.

- **miss_data**: The `miss_data` function will impute missing data in the data frame using one of mean or median methods.

- **baseline_fun**: The `baseline_fun` function will give users a quick check of the performance of the selected sklearn models compared to a baseline model, upon which the model can be improved. 

- **feature_select**: The `feature_select` function will remove redundant features using a forward selection iterative algorithm.

You can also find function descriptions and their use cases in [package vignettes](https://htmlpreview.github.io/?https://raw.githubusercontent.com/UBC-MDS/easymlr/main/docs/articles/my-vignette.html).

## Documentation

- [Vignettes](https://htmlpreview.github.io/?https://raw.githubusercontent.com/UBC-MDS/easymlr/main/docs/articles/my-vignette.html)

## Usage Example

This is a basic example demonstration of how users may use the `easymlr` package.

``` R
library(easymlr)

library(MASS)
attach(Boston)
data <- Boston
X <- data [,0:13]
Y <- as.data.frame(data [,14])
y <- data [,14]

eda_results <- eda_analysis(X)

# SAMPLE OUTPUT
#> eda_analysis(X)
#$data_head
#        crim zn indus chas   nox    rm   age    dis rad tax ptratio  black lstat
#415 45.74610  0 18.10    0 0.693 4.519 100.0 1.6582  24 666    20.2  88.27 36.98
#463  6.65492  0 18.10    0 0.713 6.317  83.0 2.7344  24 666    20.2 396.90 13.99
#179  0.06642  0  4.05    0 0.510 6.860  74.4 2.9153   5 296    16.6 391.27  6.92
#14   0.62976  0  8.14    0 0.538 5.949  61.8 4.7075   4 307    21.0 396.90  8.26
#195  0.01439 60  2.93    0 0.401 6.604  18.8 6.2196   1 265    15.6 376.70  4.38
#426 15.86030  0 18.10    0 0.679 5.896  95.4 1.9096  24 666    20.2   7.68 24.39

imputed_data <- miss_data(data, data, 'mean')

# SAMPLE OUTPUT
# imputed_df[[1]][1,]
#     crim zn indus chas   nox    rm  age    dis rad tax ptratio  black lstat medv
#1 0.25915 33  9.69    1 0.538 6.208 77.7 3.1992   5 330    19.1 391.43 11.38 21.2

baseline_model <- baseline_fun(X, Y, type = 'regression')
# SAMPLE OUTPUT - LINEAR REGRESSION MODEL SUMMARU
# baseline_model
#  RMSE     Rsquared   MAE     
#  4.86746  0.7202505  3.424126

best_features <- feature_select(X, y, threshold=0.05)
#> best_features
#[1] "lstat"   "black"   "ptratio"
```

## Relevance to the R Ecosystem

There are some packages that help with missing data imputation in the R-ecosystem such as Hmisc, missForest, Amelia and mice. There are also some packages that help feature selection suc as CARET package. However, to our knowledge, there is no general-purpose library for performing the above task in the R ecosystem.

## Dependencies

-  R version 4.0.3

| Package                                                                   | Minimum Supported Version |
| ------------------------------------------------------------------------- | ------------------------- |
| [tidyverse](https://cran.r-project.org/web/packages/tidyverse/index.html) | 0.8.3              |       
| [rlist](https://cran.r-project.org/web/packages/rlist/index.html)         | 	0.4.6.1          |
| [testthat](https://cran.r-project.org/web/packages/testthat/index.html)   | 2.3.1              |
| [MASS](https://cran.r-project.org/web/packages/MASS/index.html)       | 7.3                  |


## Contributors

Development leaders:

    Ifeanyi Anene
    Lara Habashy
    Sakshi Jain
    Zhenrui Yu
    
## Code of conduct 

Please ensure to adhere to the [code of conduct](https://github.com/UBC-MDS/easymlr/blob/main/CODE_OF_CONDUCT.md) if you would like to contrtibute to this project.

## Contributors

We welcome and recognize all contributions. You can see a list of current contributors in the contributors tab. If you would like to contribute, please view our [contributing guidelines](https://github.com/UBC-MDS/524_easysklearn/blob/main/CONTRIBUTING.rst) and get familiar with the [Github flow](https://blog.programster.org/git-workflows) workflow.

